\chapter{\centering Introduction}


\section{Problem Statement}
Saigon is a diverse city with many people from all over Vietnam flocking to it
every year, and with that comes a lot of traffic. This result in a diverse set
of license plate can be found in the city and the surrounding area. This mean that
there is a rising need to keep track of the vehicle that are operating Saigon, 
the purpose of this is to create surveys or statistics for the relevant governmental 
bureaus. \\

The traditional way of doing this is to look in the official records of the 
license plate registered in the city and deduct the actual statistic. However, 
there are many problems with this method. First, the official records are not always 
accurate in the sense that the number of bikes can move in and out of the city 
dynamically. Second, the official records are not always up to date. \\

This requires that a new, cheap, fast method to keep track of the vehicle in the city 
is needed. 

\section{Application}
Using YoloV5 running on a server computer and a mobile phone paired via QR code 
which acted as the input sensor for the model we can accurately capture and identity 
license plate on the fly in real-time.

\section{Objective}
The objective is to create something that is relatively cheap and easy to operate 
in real-time to keep track of the vehicle's origin in the city. For example the 
user can use their main camera of their phone to scan the license plate of the target 
vehicle, and it would display on screen where was the vehicle registered.



